MPLS Virtual Private Networks

### 2013-10-03 Compiled/chapter6/main.tex
fixes to c6

Fig.~\ref{fig:mpls-slides-12} shows the output of command {\tt show ip bgp vpnv4 
all} on router LER1. This command has the same effect of {\tt show ip bgp} but 
it shows the routing entries related to IPv4 VPNs. In this case the output highlights 
that LER1, in addition to its locally originated prefixes 10.0.0.0/24 with Route Distinguisher 100:1 and 193.1.1.0/24 with Route Distinguisher 100:2, knows two remote prefixes. Namely, it knows 200.1.6.0 with 
Route Distinguisher 100:11 and 193.1.1.0/24 with Route Distinguisher 100:22.
\end{shaded}

@@

 \item The P in the MPLS acronym stands for ``Private''. However, MPLS VPNs are only private at routing level: no authentication, confidentiality, or integrity is provided by the architecture. For instance, the provider can inspect all customers' traffic in plaintext. Even worse, since the separation is enforced at the routing level, it turns out that the ability of guaranteeing isolation within the same VPN actually depends on the provider's topology~\cite{integrity}.

>>>>

Fig.~\ref{fig:mpls-slides-12} shows the output of command {\tt show ip bgp vpnv4 
all} on router LER1. This command has the same effect of {\tt show ip bgp} but 
it shows the routing entries related to IPv4 VPNs. In this case the output 
highlights that LER1, in addition to its locally originated prefixes 10.0.0.0/24 
with Route Distinguisher 100:11 and 193.1.1.0/24 with Route Distinguisher 
100:22, knows two remote prefixes. Namely, it knows 200.1.6.0/24 with Route 
Distinguisher 100:11 and 10.0.0.0/24 with Route Distinguisher 100:22.
\end{shaded}

@@

 \item The P in the VPN acronym stands for ``Private''. However, MPLS VPNs are only private at routing level: no authentication, confidentiality, or integrity is provided by the architecture. For instance, the provider can inspect all customers' traffic in plaintext. Even worse, since the separation is enforced at the routing level, it turns out that the ability of guaranteeing isolation within the same VPN actually depends on the provider's topology~\cite{integrity}.
